# (PART) IRB Supplemental {-}

# Survey language and questions {-}

## Email to prospective participants {- #email-to-participants}

Read the latest version of the recruiting email text (`survey_recruiting_email.txt`):

```{r}
survey_recruiting_email <- readr::read_file("survey_recruiting_email.txt")
```

And then display it:

`r survey_recruiting_email`

## Survey introduction {- #survey_intro}

Read the lastest version of the introduction to the survey (`survey_intro.txt`):

```{r}
survey_intro <- readr::read_file("survey_intro.txt")
```

Display the survey intro:

`r survey_intro`

## Survey questions {- #survey-questions}

**Note**: Here is a useful reference for what language to use for Likert scale questions <https://www.extension.iastate.edu/documents/anr/likertscaleexamplesforsurveys.pdf>

Read the survey questions from the most recent copy of the downloaded dataset.

```{r}
suppressPackageStartupMessages(library("tidyverse")) # for pipe %>% operator

# Read local copy of survey
survey <- readr::read_csv("csv/open-science-survey-2022-fall.csv")

# Drop the Timestamp since it is provided by Google Forms automatically
survey_questions <- names(survey)[2:dim(survey)[2]]

survey_questions %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_classic(.)
```

Let's export these questions for transparency and to use as an attachment for IRB submissions:

```{r}
fileConn3 <- file("survey_questions.txt")
writeLines(survey_questions, fileConn3)
close(fileConn3)
```

::: {.todo_box}
**TODO**: Use the Google API to upload and download questions.
:::
