# Data Gathering and Cleaning {-}

## Set-up {-}

We ensure that all package dependencies are installed.

```{r set-up}
if (!require(tidyverse)) {
  install.packages("tidyverse")
}
if (!require(googledrive)) {
  install.packages("googledrive")
}

suppressPackageStartupMessages(library("tidyverse")) # for pipe %>%
```

## Download data {-}

The survey was generated and data collected using Google Forms.
The survey questions are here: <https://forms.gle/oT2ekzCsw7KVU8YU8>

We first download the data file from the spreadsheet generated by the Google Form into a comma-separated value (CSV) file in a local directory called `csv/`.

To do so, we must authenticate to Google.
For the time being, you must run `googledrive:drive_auth()` at the console, separate from rendering the protocol via `bookdown::render_book()`.

```{r eval=FALSE}
googledrive::drive_auth()
```

```{r}
if (!dir.exists('csv')) {
  dir.create('csv')
}

if (!file.exists(params$csv_fn)) {
  no_current_csv <- TRUE
  csv_fn <- "csv/open-science-survey-2022-fall.csv"
} else {
  csv_fn <- params$csv_fn
  no_current_csv <- FALSE
}

if (params$update_google_sheet || no_current_csv) {
  googledrive::drive_download(
    file = params$google_sheet_fn,
    path = csv_fn,
    type = 'csv',
    overwrite = TRUE
  )
}
```

## Load data {-}

Load the data file.

```{r}
if (file.exists(params$csv_fn)) {
  survey <- readr::read_csv(params$csv_fn, show_col_types = FALSE)
} else {
  message("File not found: ", params$csv_fn)
  survey <- NULL
}
```

There are $n=$ `r dim(survey)[1]` responses.

## Clean data {-}

Examine the variable names.

```{r}
if (is.null(survey)) {
  warning("Error loading data file")
} else {
  names(survey)
}
```

Let's rename them.

```{r}
full_questions <- names(survey)

short_names <- c(
  "timestamp",
  "campus",
  "department",
  "position",
  "years_since_degree",
  "data_types",
  "restricted_data",
  "storage_active_projects",
  "importance_sharing_collab",
  "convenience_sharing_collab",
  "barriers_sharing_collab",
  "importance_share_community",
  "barriers_share_community",
  "funders_require_data_sharing",
  "journals_require_data_sharing",
  "where_shared_community",
  "equipped_data_mgmt_sharing",
  "create_analysis_code",
  "share_analysis_code_collab",
  "create_other_code",
  "use_code_sharing_tools",
  "funders_require_code_sharing",
  "journals_require_code_sharing",
  "share_materials_community",
  "knowledge_open_science",
  "awareness_FAIR",
  "apply_FAIR",
  "heardof_reproducibility_crisis",
  "my_area_reproducibility_crisis",
  "benefit_psu_center",
  "service_psu_center",
  "comments",
  "contact_info",
  "highest_degree_earned",
  "share_analysis_code_community"
)

if (length(short_names) == length(names(survey))) {
  names(survey) <- short_names
} else {
  message("Name vector lengths differ; no change made.")
}
```

Some of the variables have values that are easy to parse, while others are more challenging, `data_types` for example.

### Modify `timestamp` {-}

Make a standard date_time format.

```{r}
survey <- survey %>%
  dplyr::mutate(., timestamp = lubridate::mdy_hms(timestamp, tz = "America/New_York"))
```

### Modify `campus` {-}

Make all campus locations lowercase and replace white space with underscores.

```{r}
survey <- survey %>%
  dplyr::mutate(., campus = tolower(campus)) %>%
  dplyr::mutate(., campus = stringr::str_replace(campus, " ", "_"))
```

### Modify `department` {-}

```{r}
survey <- survey %>%
  dplyr::mutate(
    .,
    department = recode(
      department,
      `pscyhology` = "Psychology",
      `CLA Economics` = "Economics",
      `SOCIOLOGY` = "Sociology",
      `Soc/Crim` = "Sociology",
      `Political Science / Liberal Arts` = "Political Science",
      `GSLL` = "Germanic and Slavic Languages",
      `School of Labor and Employment Relations` = "Labor and Employment Relations",
      `PLSC` = "Political Science",
      `Spanish, Italian & Portuguese` = "Spanish, Italian, and Portuguese",
      `You’ve said we can choose to omit items. What` = "Liberal Arts"
    )
  ) %>%
  dplyr::mutate(., department = tolower(department))
```

### Modify `position` {-}

Make lowercase, replace spaces and dash with underscore.

```{r}
survey <- survey %>%
  dplyr::mutate(., position = tolower(position)) %>%
  dplyr::mutate(., position = stringr::str_replace_all(position, "[ -]", "_"))
```

### Modify `years_since_degree` {-}

::: {.rmdtip}

**TODO**: Make ordinal

:::

### Modify `data_types` {-}

```{r}
survey <- survey %>%
  dplyr::mutate(., collect_audio = stringr::str_detect(data_types, "Audio files")) %>%
  dplyr::mutate(., collect_video = stringr::str_detect(data_types, "Video files")) %>%
  dplyr::mutate(
    .,
    collect_photos = stringr::str_detect(data_types, "Digital photographs and/or other images")
  ) %>%
  dplyr::mutate(
    .,
    collect_computer_data = stringr::str_detect(
      data_types,
      "Data automatically generated from or by computer programs"
    )
  ) %>%
  dplyr::mutate(.,
                collect_sensor = stringr::str_detect(data_types, "Data collected from sensors")) %>%
  dplyr::mutate(.,
                collect_docs = stringr::str_detect(data_types, "Documents or reports")) %>%
  dplyr::mutate(.,
                collect_models = stringr::str_detect(data_types, "Models/algorithms")) %>%
  dplyr::mutate(., collect_obs = stringr::str_detect(data_types, "Observational data")) %>%
  dplyr::mutate(
    .,
    collect_sims = stringr::str_detect(data_types, "Simulation data, models, and software code")
  ) %>%
  dplyr::mutate(
    .,
    collect_procedures = stringr::str_detect(data_types, "Standard operating procedures and protocols")
  ) %>%
  dplyr::mutate(., collect_txt = stringr::str_detect(data_types, "Text files")) %>%
  dplyr::mutate(., collect_genomic = stringr::str_detect(data_types, "Genomic")) %>%
  dplyr::mutate(., collect_image = stringr::str_detect(data_types, "Image data")) %>%
  dplyr::mutate(., collect_surveys = stringr::str_detect(data_types, "Survey results")) %>%
  dplyr::mutate(.,
                collect_spreadsheets = stringr::str_detect(data_types, "Spreadsheets")) %>%
  dplyr::mutate(.,
                collect_interviews = stringr::str_detect(data_types, "interview transcripts")) %>%
  dplyr::mutate(.,
                collect_gis = stringr::str_detect(data_types, "Geographic Information Systems")) %>%
  dplyr::mutate(.,
                collect_sketches = stringr::str_detect(data_types, "Sketches, diaries in digital form")) %>%
  dplyr::mutate(.,
                collect_vr = stringr::str_detect(data_types, "Virtual reality, 3D models")) %>%
  dplyr::mutate(.,
                collect_xml_json = stringr::str_detect(data_types, "Structured text files")) %>%
  dplyr::mutate(.,
                collect_web_social = stringr::str_detect(data_types, "Websites and blogs"))
  
```

### Modify `restricted_data` {-}

```{r}
survey <- survey %>%
  dplyr::mutate(., restricted_ethical = stringr::str_detect(restricted_data, "ethical concerns"),
                restricted_legal_ip = stringr::str_detect(restricted_data, "legal/intellectual"),
                restricted_sponsor = stringr::str_detect(restricted_data, "contractual restrictions"),
                restricted_none = str_detect(restricted_data, "No; My data are not restricted"))
```

### Modify `storage_active_projects` {-}

::: {.rmdtip}

**TODO**: Handle other options

:::

```{r}
survey <- survey %>%
  dplyr::mutate(.,
                store_usb = stringr::str_detect(storage_active_projects,
                                                "External USB or flash drive")) %>%
  dplyr::mutate(.,
                store_lab = stringr::str_detect(storage_active_projects,
                                                "Personal/lab computer")) %>%
  dplyr::mutate(
    .,
    store_server = stringr::str_detect(storage_active_projects,
                                       "Departmental/college server")
  ) %>%
  dplyr::mutate(.,
                store_icds = stringr::str_detect(storage_active_projects,
                                                 "ICDS/ROAR allocation")) %>%
  dplyr::mutate(
    .,
    store_onedrive = stringr::str_detect(storage_active_projects,
                                         "Microsoft OneDrive/SharePoint")
  ) %>%
  dplyr::mutate(.,
                store_googledrive = stringr::str_detect(storage_active_projects,
                                                        "Google Drive")) %>%
  dplyr::mutate(.,
                store_dropbox = stringr::str_detect(storage_active_projects,
                                                    "Dropbox")) %>%
  dplyr::mutate(., store_box = stringr::str_detect(storage_active_projects,
                                                   "Box"))
```

### Modify `barriers_sharing_collab`

::: {.rmdtip}

**TODO**: Clean these.

:::

### Modify `barriers_share_community` {-}

::: {.rmdtip}

**TODO**: Handle "other" cases.

:::

```{r}
survey <- survey %>%
  dplyr::mutate(
    .,
    barriers_sharing_security = stringr::str_detect(
      barriers_share_community,
      "Ensuring security/restricting access"
    )
  ) %>%
  dplyr::mutate(
    .,
    barriers_sharing_curation = stringr::str_detect(
      barriers_share_community,
      "Taking time to curate, organize, document data"
    )
  ) %>%
  dplyr::mutate(
    .,
    barriers_sharing_alter_before_share = stringr::str_detect(
      barriers_share_community,
      "Altering data to make it suitable to share"
    )
  ) %>%
  dplyr::mutate(
    .,
    barriers_sharing_resources = stringr::str_detect(barriers_share_community,
                                                     "Insufficient resources for sharing")
  ) %>%
  dplyr::mutate(
    .,
    barriers_sharing_staff = stringr::str_detect(
      barriers_share_community,
      "Lack of available or knowledgeable staff"
    )
)
```

### Modify `where_shared_community` {-}

```{r}
survey <- survey %>%
  dplyr::mutate(
    .,
    share_inst_repo = stringr::str_detect(where_shared_community,
                                          "Institutional repository")
  ) %>%
  dplyr::mutate(
    .,
    share_journal_suppl = stringr::str_detect(
      where_shared_community,
      "Supplemental material linked to journal article"
    )
  ) %>%
  dplyr::mutate(.,
                share_lab_web = stringr::str_detect(where_shared_community,
                                                    "Lab/project website")) %>%
  dplyr::mutate(.,
                share_ext_repo = stringr::str_detect(where_shared_community,
                                                     "External data repository")) %>%
  dplyr::mutate(
    .,
    share_govt_repo = stringr::str_detect(where_shared_community,
                                          "Government data repository")
  ) %>%
  dplyr::mutate(.,
                share_consortia = stringr::str_detect(where_shared_community,
                                                      "Research consortia"))
```

### Modify `knowledge_open_science`

```{r}
survey <- survey %>%
  dplyr::mutate(
    .,
    knowledge_open_science = recode(
      knowledge_open_science,
      `No experience/knowledge` = "None",
      `Limited experience/knowledge` = "Limited",
      `Some experience/knowledge` = "Some",
      `Considerable experience/knowledge` = "Considerable",
      `Extensive experience/knowledge` = "Extensive"
    )
  )
```

### Modify `awareness_FAIR`

```{r}
survey <- survey %>%
  dplyr::mutate(
    .,
    awareness_FAIR = recode(
      knowledge_open_science,
      `No awareness` = "None",
      `Limited awareness` = "Limited",
      `Some awareness` = "Some",
      `Considerable awareness` = "Considerable",
      `Extensive awareness` = "Extensive"
    )
  )
```

### Modify `benefit_psu_center`

```{r}
survey <- survey %>%
  dplyr::mutate(
    .,
    awareness_FAIR = recode(
      knowledge_open_science,
      `No benefit` = "None",
      `Minimal benefit` = "Minimal",
      `Some benefit` = "Some",
      `Considerable benefit` = "Considerable",
      `Extensive benefit` = "Extensive"
    )
  )
```


### Modify `service_psu_center`

```{r}
survey <- survey %>%
  dplyr::mutate(
    .,
    help_data_review_qa = stringr::str_detect(service_psu_center,
                                          "Data review and quality")
  ) %>%
  dplyr::mutate(
    .,
    help_data_mgmt_plan = stringr::str_detect(service_psu_center,
                                          "Data management plan")
  ) %>%
  dplyr::mutate(
    .,
    help_data_doc = stringr::str_detect(service_psu_center,
                                          "Data documentation")
  ) %>%
  dplyr::mutate(
    .,
    help_data_analysis_verif = stringr::str_detect(service_psu_center,
                                          "Third party verification")
  ) %>%  
  dplyr::mutate(
    .,
    help_student_staff_train = stringr::str_detect(service_psu_center,
                                          "Training and technical assistance")
  )  %>%
  dplyr::mutate(
    .,
    help_data_deidentif = stringr::str_detect(service_psu_center,
                                          "De-identification or anonymization")
  ) %>%
  dplyr::mutate(
    .,
    help_funder_compliance = stringr::str_detect(service_psu_center,
                                          "Ensuring compliance with funding")
  ) %>%
  dplyr::mutate(
    .,
    help_where_to_share = stringr::str_detect(service_psu_center,
                                          "recommendation of suitable")
  )
 
```

## Re-export cleaned data {-}

```{r}
readr::write_csv(survey, "csv/open-science-survey-2022-fall-clean.csv")
```

## Select and export contact data for follow-up

```{r}
contact_info <- survey %>%
  dplyr::select(., contact_info) %>%
  dplyr::filter(., !is.na(contact_info))

readr::write_csv(contact_info, "csv/open-science-survey-2022-fall-contact-info.csv")
```
