# Data Visualization {-}

This is a placeholder for our eventual data visualization code and commentary.

::: {.rmdtip}

**TODO** Add question by question visualizations.

:::

## Penn State campus {-}

```{r, fig.cap="What Penn State campus do you represent?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(campus) +
  ggplot2::geom_bar()
```
## Primary department or unit {-}

::: {.rmdtip}

**TODO** Normalize these before plotting.

:::

## Position {-}

```{r, fig.cap="What is your position at Penn State?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(position) +
  ggplot2::geom_bar()
```

## Highest post-secondary degree {-}

```{r, fig.cap="What is the highest post-secondary degree you have earned?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(highest_degree_earned) +
  ggplot2::geom_bar()
```

## Years since highest degree {-}

```{r, fig.cap="How many years have passed since you completed that degree?"}
survey %>%
  dplyr::mutate(., years_since_degree = factor(years_since_degree, c("< 2 years", "2-5 years", "5-10 years", "10+"), ordered = TRUE)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(years_since_degree) +
  ggplot2::geom_bar()
```

## Primary types of data {-}

::: {.rmdtip}

**TODO** Recode these in data gathering and cleaning.

:::

## Restricted data {-}

::: {.rmdtip}

**TODO** Recode these in data gathering and cleaning.

:::

```{r, fig.cap="Do you collect data that have legal or ethical restrictions governing who may access it or how it may be used?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(restricted_data) +
  ggplot2::geom_bar()
```

## Where store data for active projects? {-}

::: {.rmdtip}

**TODO** Recode these in data gathering and cleaning.

:::

## Importance of sharing with research collaborators {-}

```{r, fig.cap="How important to you is sharing data from active projects with research collaborators at Penn State or outside of Penn State?"}
survey %>%
  dplyr::mutate(., importance_sharing_collab = factor(importance_sharing_collab, 
                                                      c("Not Important", "Slightly important", 
                                                        "Moderately important", "Important", "Very important"))) %>%
  ggplot2::ggplot() +
  ggplot2::aes(importance_sharing_collab) +
  ggplot2::geom_bar()
```

## Convenience of sharing with research collaborators {-}

```{r}
survey %>%
  dplyr::mutate(., convenience_sharing_collab = factor(convenience_sharing_collab, 
                                                      c("Very inconvenient", "Inconvenient", 
                                                        "Neither convenient or inconvenient", "Convenient", "Very convenient", "Not applicable"))) %>%
  ggplot2::ggplot() +
  ggplot2::aes(convenience_sharing_collab) +
  ggplot2::geom_bar()
```

## Importance of sharing with research community {-}

```{r, fig.cap="How important to you is sharing data from completed projects with the broader research community (i.e., not direct collaborators)?"}
survey %>%
  dplyr::mutate(., importance_share_community = factor(importance_share_community, 
                                                      c("Not Important", "Slightly important", 
                                                        "Moderately important", "Important", "Very important"))) %>%
  ggplot2::ggplot() +
  ggplot2::aes(importance_share_community) +
  ggplot2::geom_bar()
```

## Obstacles to sharing more broadly {-}

::: {.rmdtip}

**TODO** Recode these in data gathering and cleaning.

:::

## Requirements for data sharing from funders {-}

```{r, fig.cap="Do research sponsors/funders in your field require data sharing?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(funders_require_data_sharing) +
  ggplot2::geom_bar()
```

## Requirements for data sharing from journals {-}

```{r, fig.cap="Do journals in your field require data sharing?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(journals_require_data_sharing) +
  ggplot2::geom_bar()
```

## Where has data been shared? {-}

::: {.rmdtip}

**TODO** Recode these in data gathering and cleaning.

:::

## How well-equipped are we to meet data management and sharing requirements? {-}

```{r, fig.cap="How well-equipped do you feel you, your colleagues, and trainees are to meet data management and sharing requirements of sponsors/funders or journals?"}
survey %>%
  dplyr::mutate(., equipped_data_mgmt_sharing = factor(equipped_data_mgmt_sharing, 
                                                      c("Not equipped at all", "Slightly equipped", 
                                                        "Moderately equipped", "Equipped", "Very well equipped"))) %>%
  ggplot2::ggplot() +
  ggplot2::aes(equipped_data_mgmt_sharing) +
  ggplot2::geom_bar()
```

## Frequency of code generation {-}

```{r, fig.cap="How often do you create computer scripts or data analysis code in the conduct of your research?"}
survey %>%
  dplyr::mutate(., create_analysis_code = factor(create_analysis_code, 
                                                      c("Never", "Rarely", 
                                                        "Sometimes", "Often", "Always"))) %>%
  ggplot2::ggplot() +
  ggplot2::aes(create_analysis_code) +
  ggplot2::geom_bar()
```

## Frequency of code sharing with collaborators {-}

```{r, fig.cap = "How often do you share computer scripts or data analysis code with direct research collaborators ?"}
survey %>%
  dplyr::mutate(., share_analysis_code_collab = factor(share_analysis_code_collab, 
                                                      c("Never", "Rarely", 
                                                        "Sometimes", "Often", "Always"))) %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_analysis_code_collab) +
  ggplot2::geom_bar()
```
## Frequency of use of open source code-sharing tools {-}

```{r, fig.cap="How often do you use open source code sharing tools (e.g., GitHub, GitLab, BitBucket)?"}
survey %>%
  dplyr::mutate(., use_code_sharing_tools = factor(use_code_sharing_tools, 
                                                      c("Never", "Rarely", 
                                                        "Sometimes", "Often", "Always"))) %>%
  ggplot2::ggplot() +
  ggplot2::aes(use_code_sharing_tools) +
  ggplot2::geom_bar()
```

## Frequency of open code sharing {-}

```{r, fig.cap="How often do you share computer scripts or data analysis code openly?"}
survey %>%
  dplyr::mutate(.,
                share_analysis_code_community = factor(
                  share_analysis_code_community,
                  c("Never", "Rarely",
                    "Sometimes", "Often", "Always")
                )) %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_analysis_code_community) +
  ggplot2::geom_bar()
```

## Creation of other types of software {-}

```{r, fig.cap="Do you create other kinds of software in the conduct of your research?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(create_other_code) +
  ggplot2::geom_bar()
```

## Requirements for code sharing from funders {-}

```{r, fig.cap="Do sponsors/funders in your field require code sharing?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(funders_require_code_sharing) +
  ggplot2::geom_bar()
```

## Requirements for code sharing from journals {-}

```{r, fig.cap="Do journals in your field require code sharing?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(journals_require_code_sharing) +
  ggplot2::geom_bar()
```

## Experience/Knowledge of Open Science {-}

::: {.rmdtip}

**TODO** Recode these.

:::

```{r, fig.cap="What is your experience with/knowledge of open science practices?"}
survey %>%
  dplyr::mutate(.,
                knowledge_open_science = factor(
                  knowledge_open_science,
                  c("No experience/knowledge", "Limited experience/knowledge",
                    "Some experience/knowledge", "Considerable experience/knowledge", "Extensive experience/knowledge")
                )) %>%
  ggplot2::ggplot() +
  ggplot2::aes(knowledge_open_science) +
  ggplot2::geom_bar()
```

## Awareness of FAIR principles {-}

```{r, fig.cap="Describe your awareness of the FAIR (findable, accessible, interoperable, reusable) principles pertaining to research data."}
survey %>%
  dplyr::mutate(.,
                awareness_FAIR = factor(
                  awareness_FAIR,
                  c("No awareness", "Limited awareness",
                    "Some awareness", "Considerable awareness", "Extensive awareness")
                )) %>%
  ggplot2::ggplot() +
  ggplot2::aes(awareness_FAIR) +
  ggplot2::geom_bar()
```

## Application of FAIR principles in your own work {-}

```{r, fig.cap="Do you apply FAIR principles in your own data management and sharing practices?"}
survey %>%
  dplyr::mutate(.,
                apply_FAIR = factor(
                  apply_FAIR,
                  c("Never", "Rarely",
                    "Sometimes", "Often", "Always", "Not applicable")
                )) %>%
  ggplot2::ggplot() +
  ggplot2::aes(apply_FAIR) +
  ggplot2::geom_bar()
```

## Heard of reproducibility crisis? {-}

```{r, fig.cap="Have you heard of the 'reproducibility crisis' in science?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(heardof_reproducibility_crisis) +
  ggplot2::geom_bar()
```

## Is there a crisis in your area? {-}

```{r, fig.cap="Is there a reproducibility crisis in your area of research?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(my_area_reproducibility_crisis) +
  ggplot2::geom_bar()
```

## Benefit from PSU center

```{r, fig.cap="How much benefit would you derive from a center at Penn State focused on supporting the adoption of best practices in data management and sharing, code sharing, open science, and reproducible research?"}

survey %>%
  dplyr::mutate(.,
                benefit_psu_center = factor(
                  benefit_psu_center,
                  c("No benefit", "Minimal benefit",
                    "Some benefit", "Considerable benefit", "Extensive benefit", "Not applicable")
                )) %>%
  ggplot2::ggplot() +
  ggplot2::aes(benefit_psu_center) +
  ggplot2::geom_bar()

```

## Services from PSU Center


::: {.rmdtip}

**TODO** Create plot.

:::

## Comments

```{r}
survey %>%
  dplyr::filter(., !is.na(comments)) %>%
  dplyr::select(., comments) %>%
  knitr::kable(format = 'html')
```

