# Data Visualization {-}

The following shows simple visualizations of the survey data.

## Filter "test" responses {-}

The responses prior to 2022-12-22 were used to test the survey, and aren't really data.

```{r}
survey <- survey %>%
  dplyr::filter(., timestamp > lubridate::as_date("2022-12-22"))
```

There are $n=$ `r dim(survey_qs_df)[1]` questions in total.

As of `r Sys.Date()`, we have had $n$= `r dim(survey)[1]` responses.

## Penn State campus {-}

> `r paste0("Question ", survey_qs_df$q_num[1], ": ", survey_qs_df$question[1])` 

```{r fig-campus, fig.cap="What Penn State campus do you represent?"}
survey %>%
  dplyr::filter(., !is.na(campus)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(campus) +
  ggplot2::geom_bar()
```

## Primary department or unit {-}

> `r paste0("Question ", survey_qs_df$q_num[2], ": ", survey_qs_df$question[2])` 

::: {.rmdtip}

**TODO** Normalize these before plotting.

:::

## Position {-}

> `r paste0("Question ", survey_qs_df$q_num[3], ": ", survey_qs_df$question[3])` 

```{r fig-position, fig.cap="What is your position at Penn State?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(position) +
  ggplot2::geom_bar()
```

## Highest post-secondary degree {-}

> `r paste0("Question ", survey_qs_df$q_num[33], ": ", survey_qs_df$question[33])` 

```{r fig-highest-degree, fig.cap="What is the highest post-secondary degree you have earned?"}
survey %>%
  dplyr::filter(., !is.na(highest_degree_earned)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(highest_degree_earned) +
  ggplot2::geom_bar()
```

## Years since highest degree {-}

> `r paste0("Question ", survey_qs_df$q_num[4], ": ", survey_qs_df$question[4])` 

```{r fig-yrs-since-degree, fig.cap="How many years have passed since you completed that degree?"}
survey %>%
  dplyr::mutate(., years_since_degree = factor(
    years_since_degree,
    c("< 2 years", "2-5 years", "5-10 years", "10+"),
    ordered = TRUE
  )) %>%
  dplyr::filter(., !is.na(years_since_degree)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(years_since_degree) +
  ggplot2::geom_bar()
```

## Primary types of data {-}

> `r paste0("Question ", survey_qs_df$q_num[5], ": ", survey_qs_df$question[5])` 

::: {.rmdnote}

**TODO:** Create plots

:::

## Restricted data {-}

> `r paste0("Question ", survey_qs_df$q_num[6], ": ", survey_qs_df$question[6])` 

```{r restricted-data-preprocess, fig.cap="Respondents who collect restricted data of varied types"}
restricted <- survey %>%
  dplyr::select(., -restricted_data) %>%
  tidyr::pivot_longer(., cols = contains("restricted"), 
                      names_to = "restricted_data_types", 
                      values_to = "restricted_data_vals") %>%
  dplyr::mutate(., restricted_data_types = str_remove(restricted_data_types, "restricted_"))

restricted %>%
  ggplot2::ggplot() +
  ggplot2::aes(restricted_data_types,
               as.numeric(restricted_data_vals)) +
  ggplot2::geom_col() +
  scale_y_continuous(name = "N responses",
                     breaks = c(0:sum(restricted$restricted_data_vals))) +
  xlab("Types of restrictions") +
  coord_flip()
```

```{r fig-restricted-ethical, fig.cap="Data about human participants that are subject to restrictions due to ethical concerns", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(restricted_ethical) +
  ggplot2::geom_bar()
```

```{r fig-restricted-legal-ip, fig.cap="Data subject to legal/intellectual property restrictions", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(restricted_legal_ip) +
  ggplot2::geom_bar()
```

```{r fig-restricted-sponsor, fig.cap="Data subject to contractual restrictions from a sponsor or provider", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(restricted_sponsor) +
  ggplot2::geom_bar()
```

```{r fig-restricted-none, fig.cap="My data are not restricted in these ways", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(restricted_none) +
  ggplot2::geom_bar()
```

## Where store data for active projects? {-}

> `r paste0("Question ", survey_qs_df$q_num[7], ": ", survey_qs_df$question[7])` 

```{r fig-data-storage-places, fig.cap="Locations for storing active research data"}
storage_active <- survey %>%
  dplyr::select(., -storage_active_projects) %>%
  tidyr::pivot_longer(., cols = contains("store"), 
                      names_to = "store_where", 
                      values_to = "store_where_vals") %>%
  dplyr::mutate(., store_where = str_remove(store_where, "store_"))

storage_active %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_where,
               as.numeric(store_where_vals)) +
  ggplot2::geom_col() +
  scale_y_continuous(name = "N responses",
                     breaks = c(0:length(storage_active$store_where_vals))) +
  xlab("Where data is stored") +
  coord_flip()
```


```{r fig-store-usb, fig.cap="External USB or flash drive", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_usb) +
  ggplot2::geom_bar()
```

```{r fig-store-lab, fig.cap="Personal/lab computer", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_lab) +
  ggplot2::geom_bar()
```

```{r fig-store-server, fig.cap="Departmental/college server", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_server) +
  ggplot2::geom_bar()
```

```{r fig-store-icds, fig.cap="ICDS/ROAR allocation", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_icds) +
  ggplot2::geom_bar()
```

```{r fig-store-onedrive, fig.cap="Microsoft OneDrive/SharePoint", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_onedrive) +
  ggplot2::geom_bar()
```

```{r fig-store-googledrive, fig.cap="Google Drive", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_googledrive) +
  ggplot2::geom_bar()
```

```{r fig-store-dropbox, fig.cap="Dropbox", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_dropbox) +
  ggplot2::geom_bar()
```

```{r fig-store-box, fig.cap="Box", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(store_box) +
  ggplot2::geom_bar()
```

::: {.rmdtip}

**TODO** Recode these in data gathering and cleaning.

:::

## Importance of sharing with research collaborators {-}

> `r paste0("Question ", survey_qs_df$q_num[8], ": ", survey_qs_df$question[8])` 

```{r fig-import-share-collab, fig.cap="How important to you is sharing data from active projects with research collaborators at Penn State or outside of Penn State?"}
survey %>%
  dplyr::mutate(., importance_sharing_collab = factor(
    importance_sharing_collab,
    c(
      "Not Important",
      "Slightly important",
      "Moderately important",
      "Important",
      "Very important"
    )
  )) %>%
  dplyr::filter(., !is.na(importance_sharing_collab)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(importance_sharing_collab) +
  ggplot2::geom_bar()
```

## Convenience of sharing with research collaborators {-}

> `r paste0("Question ", survey_qs_df$q_num[9], ": ", survey_qs_df$question[9])` 

```{r fig-convenient-share-collab}
survey %>%
  dplyr::mutate(.,
                convenience_sharing_collab = factor(
                  convenience_sharing_collab,
                  c(
                    "Very inconvenient",
                    "Inconvenient",
                    "Neither",
                    "Convenient",
                    "Very convenient",
                    "Not applicable"
                  )
                )) %>%
  dplyr::filter(., !is.na(convenience_sharing_collab)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(convenience_sharing_collab) +
  ggplot2::geom_bar()
```

## Barriers to sharing with research collaborators {-}

> `r paste0("Question ", survey_qs_df$q_num[10], ": ", survey_qs_df$question[10])` 

```{r}
survey %>%
  dplyr::filter(., !is.na(barriers_sharing_collab)) %>%
  dplyr::select(., barriers_sharing_collab) %>%
  knitr::kable(format = 'html')
```

## Importance of sharing with research community {-}

> `r paste0("Question ", survey_qs_df$q_num[11], ": ", survey_qs_df$question[11])` 

```{r fig-import-share-community, fig.cap="How important to you is sharing data from completed projects with the broader research community (i.e., not direct collaborators)?"}
survey %>%
  dplyr::mutate(.,
                importance_share_community = factor(
                  importance_share_community,
                  c(
                    "Not Important",
                    "Slightly important",
                    "Moderately important",
                    "Important",
                    "Very important"
                  )
                )) %>%
  dplyr::filter(., !is.na(importance_share_community)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(importance_share_community) +
  ggplot2::geom_bar()
```

## Obstacles to sharing with research community {-}

> `r paste0("Question ", survey_qs_df$q_num[12], ": ", survey_qs_df$question[12])` 

```{r fig-obstacles-to-sharing-w-comm, fig.cap="Obstacles to sharing with research community"}
sharing_comm_obstacles <- survey %>%
  dplyr::select(.,-barriers_share_community,-barriers_sharing_collab) %>%
  tidyr::pivot_longer(
    .,
    cols = contains("barriers"),
    names_to = "barriers_comm_what",
    values_to = "barriers_comm_vals"
  ) %>%
  dplyr::mutate(., barriers_comm_what = str_remove(barriers_comm_what, "barriers_sharing_"))

sharing_comm_obstacles %>%
  ggplot2::ggplot() +
  ggplot2::aes(barriers_comm_what,
               as.numeric(barriers_comm_vals)) +
  ggplot2::geom_col() +
  scale_y_continuous(name = "N responses",
                     breaks = c(0:length(
                       sharing_comm_obstacles$barriers_comm_vals
                     ))) +
  xlab("Barriers to sharing with the research community") +
  coord_flip()
```

```{r fig-barriers-security, fig.cap="Ensuring security/restricting access", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(barriers_sharing_security) +
  ggplot2::geom_bar()
```

```{r fig-barriers-curation, fig.cap="Taking time to curate, organize, document data", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(barriers_sharing_curation) +
  ggplot2::geom_bar()
```

```{r fig-barriers-altering-data, fig.cap="Altering data to make it suitable to share", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(barriers_sharing_alter_before_share) +
  ggplot2::geom_bar()
```

```{r fig-barriers-resources, fig.cap="Insufficient resources for sharing", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(barriers_sharing_resources) +
  ggplot2::geom_bar()
```

```{r fig-barriers-staff, fig.cap="Lack of available or knowledgeable staff", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(barriers_sharing_staff) +
  ggplot2::geom_bar()
```

## Requirements for data sharing from funders {-}

> `r paste0("Question ", survey_qs_df$q_num[13], ": ", survey_qs_df$question[13])` 

```{r fig-funders-require-data-sharing, fig.cap="Do research sponsors/funders in your field require data sharing?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(funders_require_data_sharing) +
  ggplot2::geom_bar()
```

## Requirements for data sharing from journals {-}

> `r paste0("Question ", survey_qs_df$q_num[14], ": ", survey_qs_df$question[14])` 

```{r fig-journals-require-data-sharing, fig.cap="Do journals in your field require data sharing?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(journals_require_data_sharing) +
  ggplot2::geom_bar()
```

## Where has data been shared? {-}

> `r paste0("Question ", survey_qs_df$q_num[15], ": ", survey_qs_df$question[15])` 

```{r fig-where-data-shared, fig.cap="Where data has been shared"}
sharing_where <- survey %>%
  dplyr::select(.,-where_shared_community, -share_analysis_code_collab, -share_analysis_code_community) %>%
  tidyr::pivot_longer(
    .,
    cols = c('share_inst_repo', 'share_journal_suppl', 'share_lab_web', 'share_ext_repo',
             'share_govt_repo', 'share_consortia'),
    names_to = "share_where_target",
    values_to = "share_where_vals"
  ) %>%
  dplyr::mutate(., share_where_target = str_remove(share_where_target, "share_"))

sharing_where %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_where_target,
               as.numeric(share_where_vals)) +
  ggplot2::geom_col() +
  scale_y_continuous(name = "N responses",
                     breaks = c(0:length(
                       sharing_where$share_where_vals
                     ))) +
  xlab("Where data are shared") +
  coord_flip()
```

```{r fig-where-share-inst-repo, fig.cap="Share via institutional repository", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_inst_repo) +
  ggplot2::geom_bar()
```

```{r fig-where-share-journal-suppl, fig.cap="Share via journal supplement", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_journal_suppl) +
  ggplot2::geom_bar()
```

```{r fig-where-share-lab-web, fig.cap="Share via lab website", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_lab_web) +
  ggplot2::geom_bar()
```

```{r fig-where-share-ext-repo, fig.cap="Share via external data repository", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_ext_repo) +
  ggplot2::geom_bar()
```

```{r fig-where-share-govt-repo, fig.cap="Share via government data repository", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_govt_repo) +
  ggplot2::geom_bar()
```

```{r fig-where-share-consortia, fig.cap="Share via research consortium", include=FALSE}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_consortia) +
  ggplot2::geom_bar()
```

## How well-equipped are we to meet data management and sharing requirements? {-}

> `r paste0("Question ", survey_qs_df$q_num[16], ": ", survey_qs_df$question[16])` 

```{r fig-equipped-for-new-reqmts, fig.cap="How well-equipped do you feel you, your colleagues, and trainees are to meet data management and sharing requirements of sponsors/funders or journals?"}
survey %>%
  dplyr::mutate(.,
                equipped_data_mgmt_sharing = factor(
                  equipped_data_mgmt_sharing,
                  c(
                    "Not equipped at all",
                    "Slightly equipped",
                    "Moderately equipped",
                    "Equipped",
                    "Very well equipped"
                  )
                )) %>%
  dplyr::filter(., !is.na(equipped_data_mgmt_sharing)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(equipped_data_mgmt_sharing) +
  ggplot2::geom_bar()
```

---

## Frequency of code generation {-}

> `r paste0("Question ", survey_qs_df$q_num[17], ": ", survey_qs_df$question[17])` 

```{r fig-how-often-generate-code, fig.cap="How often do you create computer scripts or data analysis code in the conduct of your research?"}
survey %>%
  dplyr::mutate(., create_analysis_code = factor(
    create_analysis_code,
    c("Never", "Rarely",
      "Sometimes", "Often", "Always")
  )) %>%
  dplyr::filter(., !is.na(create_analysis_code)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(create_analysis_code) +
  ggplot2::geom_bar()
```

## Frequency of code sharing with collaborators {-}

> `r paste0("Question ", survey_qs_df$q_num[18], ": ", survey_qs_df$question[18])` 

```{r fig-how-often-share-code, fig.cap = "How often do you share computer scripts or data analysis code with direct research collaborators ?"}
survey %>%
  dplyr::mutate(.,
                share_analysis_code_collab = factor(
                  share_analysis_code_collab,
                  c("Never", "Rarely",
                    "Sometimes", "Often", "Always")
                )) %>%
  dplyr::filter(., !is.na(share_analysis_code_collab)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_analysis_code_collab) +
  ggplot2::geom_bar()
```

## Creation of other types of software {-}

> `r paste0("Question ", survey_qs_df$q_num[19], ": ", survey_qs_df$question[19])` 

```{r fig-create-other-software, fig.cap="Do you create other kinds of software in the conduct of your research?"}
survey %>%
  ggplot2::ggplot() +
  ggplot2::aes(create_other_code) +
  ggplot2::geom_bar()
```

## Frequency of use of open source code-sharing tools {-}

> `r paste0("Question ", survey_qs_df$q_num[20], ": ", survey_qs_df$question[20])` 

```{r fig-how-often-code-sharing-tools, fig.cap="How often do you use open source code sharing tools (e.g., GitHub, GitLab, BitBucket)?"}
survey %>%
  dplyr::mutate(., use_code_sharing_tools = factor(use_code_sharing_tools, 
                                                      c("Never", "Rarely", 
                                                        "Sometimes", "Often", "Always"))) %>%
  dplyr::filter(., !is.na(use_code_sharing_tools)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(use_code_sharing_tools) +
  ggplot2::geom_bar()
```

## Requirements for code sharing from funders {-}

> `r paste0("Question ", survey_qs_df$q_num[21], ": ", survey_qs_df$question[21])` 

```{r fig-funders-require-code-sharing, fig.cap="Do sponsors/funders in your field require code sharing?"}
survey %>%
  dplyr::filter(., !is.na(funders_require_code_sharing)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(funders_require_code_sharing) +
  ggplot2::geom_bar()
```

## Requirements for code sharing from journals {-}

> `r paste0("Question ", survey_qs_df$q_num[22], ": ", survey_qs_df$question[22])` 

```{r fig-journals-require-code-sharing, fig.cap="Do journals in your field require code sharing?"}
survey %>%
  dplyr::filter(., !is.na(funders_require_code_sharing)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(journals_require_code_sharing) +
  ggplot2::geom_bar()
```

## Frequency of open code sharing {-}

> `r paste0("Question ", survey_qs_df$q_num[34], ": ", survey_qs_df$question[34])` 

```{r fig-how-often-share-code-openly, fig.cap="How often do you share computer scripts or data analysis code openly?"}
survey %>%
  dplyr::mutate(.,
                share_analysis_code_community = factor(
                  share_analysis_code_community,
                  c("Never", "Rarely",
                    "Sometimes", "Often", "Always")
                )) %>%
  dplyr::filter(., !is.na(share_analysis_code_community)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(share_analysis_code_community) +
  ggplot2::geom_bar()
```

## Share other materials {-}

> `r paste0("Question ", survey_qs_df$q_num[23], ": ", survey_qs_df$question[23])` 

::: {.rmdtip}

**TODO**: Create graphs.

:::

---

## Experience/Knowledge of Open Science {-}

> `r paste0("Question ", survey_qs_df$q_num[24], ": ", survey_qs_df$question[24])` 

::: {.rmdtip}

**TODO**: Recode these.

:::

```{r fig-experience-w-open-science, fig.cap="What is your experience with/knowledge of open science practices?"}
survey %>%
  dplyr::mutate(.,
                knowledge_open_science = factor(
                  knowledge_open_science,
                  c("No experience/knowledge", "Limited experience/knowledge",
                    "Some experience/knowledge", "Considerable experience/knowledge", "Extensive experience/knowledge")
                )) %>%
  dplyr::filter(., !is.na(knowledge_open_science)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(knowledge_open_science) +
  ggplot2::geom_bar()
```

## Awareness of FAIR principles {-}

> `r paste0("Question ", survey_qs_df$q_num[25], ": ", survey_qs_df$question[25])` 

::: {.rmdtip}

**TODO**: Recode these.

:::

```{r fig-awareness-FAIR, fig.cap="Describe your awareness of the FAIR (findable, accessible, interoperable, reusable) principles pertaining to research data."}
survey %>%
  dplyr::mutate(.,
                awareness_FAIR = factor(
                  awareness_FAIR,
                  c("No awareness", "Limited awareness",
                    "Some awareness", "Considerable awareness", "Extensive awareness")
                )) %>%
  dplyr::filter(., !is.na(awareness_FAIR)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(awareness_FAIR) +
  ggplot2::geom_bar()
```

## Application of FAIR principles in your own work {-}

> `r paste0("Question ", survey_qs_df$q_num[26], ": ", survey_qs_df$question[26])` 

```{r fig-apply-FAIR-own-research, fig.cap="Do you apply FAIR principles in your own data management and sharing practices?"}
survey %>%
  dplyr::mutate(.,
                apply_FAIR = factor(
                  apply_FAIR,
                  c("Never", "Rarely",
                    "Sometimes", "Often", "Always", "Not applicable")
                )) %>%
  dplyr::filter(., !is.na(apply_FAIR)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(apply_FAIR) +
  ggplot2::geom_bar()
```

## Heard of reproducibility crisis? {-}

> `r paste0("Question ", survey_qs_df$q_num[27], ": ", survey_qs_df$question[27])` 


```{r fig-heard-of-repro-crisis, fig.cap="Have you heard of the 'reproducibility crisis' in science?"}
survey %>%
  dplyr::filter(., !is.na(heardof_reproducibility_crisis)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(heardof_reproducibility_crisis) +
  ggplot2::geom_bar()
```

## Is there a crisis in your area? {-}

> `r paste0("Question ", survey_qs_df$q_num[28], ": ", survey_qs_df$question[28])` 

```{r fig-repro-crisis-your-area, fig.cap="Is there a reproducibility crisis in your area of research?"}
survey %>%
  dplyr::filter(., !is.na(my_area_reproducibility_crisis)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(my_area_reproducibility_crisis) +
  ggplot2::geom_bar()
```

## Benefit from PSU center {-}

> `r paste0("Question ", survey_qs_df$q_num[29], ": ", survey_qs_df$question[29])` 

```{r fig-benefit-from-psu-ctr, fig.cap="How much benefit would you derive from a center at Penn State focused on supporting the adoption of best practices in data management and sharing, code sharing, open science, and reproducible research?"}

survey %>%
  dplyr::mutate(.,
                benefit_psu_center = factor(
                  benefit_psu_center,
                  levels = c(
                    "No benefit",
                    "Minimal benefit",
                    "Some benefit",
                    "Considerable benefit",
                    "Extensive benefit",
                    "Not applicable"
                  )
                )) %>%
  dplyr::filter(., !is.na(benefit_psu_center)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(benefit_psu_center) +
  ggplot2::geom_bar()
```

## Services from PSU Center {-}

> `r paste0("Question ", survey_qs_df$q_num[30], ": ", survey_qs_df$question[30])` 

::: {.rmdtip}

**TODO** Create plot.

:::

## Comments {-}

> `r paste0("Question ", survey_qs_df$q_num[31], ": ", survey_qs_df$question[31])` 

```{r fig-comments, fig.cap="Any final comments about data management, data sharing, and open science?"}
survey %>%
  dplyr::filter(., !is.na(comments)) %>%
  dplyr::select(., comments) %>%
  knitr::kable(format = 'html')
```

