--- 
title: "Open Science at Penn State"
author: ["Rick O. Gilmore", "Frank Hillary", "Nicole Lazar", "Briana Wham"]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [include/bib/book.bib, include/bib/packages.bib]
csl: include/bib/apa.csl
url: "https://github.com/penn-state-open-science/survey-fall-2022"
description: |
  This is the protocol for the Fall 2022 survey on Open Science.
link-citations: yes
github-repo: "penn-state-open-science/survey-fall-2022"
params:
  update_google_sheet: true
  google_sheet_fn: 'C-ORR Survey 2022 Fall (Responses)'
  csv_fn: "csv/open-science-survey-2022-fall.csv"
  irb_id: "STUDY00021455"
  irb_long_name: "Knowledge about and attitudes toward open science practices among Penn State researchers"
  irb_short_name: "Open science at Penn State"
  pi_name: 'Rick Gilmore'
  pi_phone: '814-865-3664'
  pi_email: 'rog1@psu.edu'
  pi_dept: 'Psychology'
---

```{r}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center",
                      fig.path = "include/img/")
library(tidyverse)
source("../R/functions.R")
```

# About {-}

This is a research protocol for *`r params$irb_long_name`*, `r params$irb_id` (`r params$irb_short_name`) written in **Markdown**.

It also represents an exercise in how to use git-based version control, Rmarkdown, and the `bookdown` package to create an open research protocol that also addresses questions required for the Penn State IRB's protocol review process. 
Our goal is to reduce duplication of effort and to demonstrate how an IRB research application might also be used as a living, version-controlled, research protocol.

These materials may be copied and reused by anyone.

By default, we do *not* update the data from Google Drive (`params$update_google_sheet==FALSE`).

```{r update-data, include=FALSE, eval=FALSE}
if (!file.exists(params$csv_fn)) {
  no_current_csv <- TRUE
  csv_fn <- "csv/open-science-survey-2022-fall.csv"
} else {
  csv_fn <- params$csv_fn
  no_current_csv <- FALSE
}

if (params$update_google_sheet || no_current_csv) {
  googledrive::drive_download(
    file = params$google_sheet_fn,
    path = csv_fn,
    type = 'csv',
    overwrite = TRUE
  )
}
```

```{r add-bib-entries, include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'include/bib/packages.bib')
```
